### 2014-05-02 Article.tex
Update Article.tex

>>>>

\section{Abstract}
In this contribution, we investigate the problem of "SwitchBoxes".
The goal is, given $n$ wires, to generate all the permutations of these wires by using "boxes", that swap two wires. We tried to minimize the number of boxes that were necessary.
We introduce a conjecture that puts our problem in relation with binary insertion sort. We successfully used a heavily optimized algorithm to prove this conjecture for small values of $n$.

\section{Introduction}
